Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-17 paper/v2/paper-edited.tex
minor changes to 5

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  %\vspace{-1em}
\end{figure*}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
  \caption{Example topology for which the \sysname policy: $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
  \label{fig:unimplementable}
  %\vspace{-1em}
\end{figure}

>>>>

  \caption{Product graph construction for policy $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  %\vspace{-1em}
\end{figure*}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
  \label{fig:unimplementable}
  %\vspace{-1em}
\end{figure}
